Finding a closest point in a lattice of Voronoi's first kind

### 2014-07-12 reviews/response.tex

We believe that it is only Theorem 3 from~\cite{ConwaySloane1992_voronoi_lattice_3d_obtuse_superbases} that needs to cited.  Theorem~2 in \cite{ConwaySloane1992_voronoi_lattice_3d_obtuse_superbases} asserts that the relevant vectors in any lattice $\Lambda$ are the shortest coset representatives of the quotient $\Lambda/2\Lambda$.  Theorem~3 uses this, Selling's formula, and the fact that the Selling parameters are nonpositive to prove that the relevant vectors in a lattice of Voronoi's first kind take the form
\[
\sum_{i \in I} b_i
\]
where $I$ is a strict subset of $\{1, 2, \dots, n+1\}$ that is not empty.

@@

\item\textbf{Comment:}  
page 15, ``there many'' $\to$ ``there may'' 
\\\textbf{Response:}
Fixed.

\item\textbf{Comment:}  
References: 
- 12: missing author (R. Raz) 
- 18: ``A V'' $\to$ ``A. V.'' etc, 
- 37: journal version in SIAM J. computing, 42(3):1364-1391 (2013) 
\\\textbf{Response:}
Fixed.

\item\textbf{Comment:}  
Some additional references on CVPP you may find interesting 
(cite at your own discretion):

- O. Regev (2004) Improved Inapproximability of Lattice and Coding Problems With Preprocessing. IEEE Transactions on Information Theory 50(9): 2031-2037 
- ``Hardness of Approximating the Closest Vector Problem with Pre-Processing'', M. Alekhnovich, S. Khot, G. Kindler, N. Vishnoi, Computational Complexity 20(4):741-753, 2011.

@@

- D. Aharonov and Oded Regev (2005). Lattice problems in NP ∩ co-NP. J. ACM 52, 749-765.

(Gives polynomial time solution to approximate the distance estimation version of CVPP within $\gamma=\sqrt(n \log n)$ approximation factor, i.e., for any lattice there is an appropriate advice (more complex than just a good basis) that allows to approximate in polynomial time the distance of any target point to the lattice within gamma, but without actually finding a nearby lattice point.)

- On the Closest Vector Problem with a Distance Guarantee 
D. Dadush, O. Regev, N. Stephens-Davidowitz, Computational Complexity Conference 2014, to appear (next week!)

I am not sure, as the paper has not appeared yet, but I suspect it is the same as the paper on Dadush webpage with title ``On BDD and CVPP''. 
See link 
http://cs.nyu.edu/~dadush/papers/cvpp.pdf 
and read abstract for more information.
\\\textbf{Response:}
We thank the reviewer for these interesting references highlighting the difficulty of computing close approximations of a closest lattice point.  These have been referenced in Section~\zref{sec:iterative-slicer} with the following text:
